Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-04-28 paper-RMDON.tex
primer parrafo :bulb:

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Rodríguez Arroyo\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica}
\thanks{\IEEEauthorrefmark{1}E-mail: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}
\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20th, 2017.}
\thanks{First draft revised on May 8th, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

% The paper headers
\markboth{Advanced Topics in Operative Systems, March~2017}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for Journals}

@@

\section{Introduction}

>>>>

\author{\IEEEauthorblockN{Raquel Elizondo\IEEEauthorrefmark{1}, Martín Flores\IEEEauthorrefmark{1}, Jose Salazar\IEEEauthorrefmark{1}, Oscar Rodríguez\IEEEauthorrefmark{1} and Nelson Méndez\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{School of Computer Science\\
Instituto Tecnológico de Costa Rica, Cartago, Costa Rica\\}
\vspace{0.1cm}
\IEEEauthorrefmark{1}\small{\emph{Email}: \textbf{\{}\texttt{rackelelizondo, mfloresg, bimbosalazar, oscar.rodar, n.mendezmontero}\textbf{\}}\texttt{@gmail.com}}

\thanks{This document was proposed as part of the \emph{Advanced Topics in Operative Systems} course at Instituto Tecnológico de Costa Rica. First Semester, 2017.} 
\thanks{Abstract and References revised on March 20th, 2017.}
\thanks{First draft revised on May 8th, 2017.}
%\thanks{Abstract and References received March 20, 2017; revised September 17, 2014. 
%Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}
}

@@

% The paper headers
\markboth{Advanced Topics in Operative Systems, May~2017}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for Journals}

@@

\section{Introduction}
\IEEEPARstart{N}{owadays} real-time applications are taking over mobile devices more than ever and, although this brings a lot of new opportunities, it brings challenges too. There is a plenty of examples of applications that includes collective, social, and distributed features out there and, it just a matter to take a look to a smartphone of an average user to see several of those in action. But, despite the success behind the cell phones as mobile devices, currently there are many other hardware architectures which has mobile capabilities as well and, in which the implementation of new and interactive applications have increased in recent years. Weareable technolgy and ARM architectures are good examples of this.
